To Compete or Cooperate? This is the Question in Communities of Autonomous Services

### 2014-01-31 papers/Exp Sys App/coop_response_letter.tex

%\documentclass[preprint,authoryear,12pt]{elsarticle}
\documentclass[times, 12pt,a4paper]{article}
\usepackage{graphicx,amssymb,amsthm,stmaryrd}%,booktabs}
\usepackage{times}
\usepackage{amsmath,url,algorithm,algorithmic,mathrsfs,makeidx}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsfig}
\usepackage{latex8}

%journal{Journal of Knowledge-Based Systems}

\begin{document}
%\begin{frontmatter}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary} {Corollary}
\title{\underline{Response Letter}\\\vspace{0.5cm}To Compete or Cooperate? This is the Question in Communities of Autonomous Services}
\author{Ehsan Khosrowshahi Asl\\
e\_khosr@encs.concordia.ca\\
\and
Jamal Bentahar\\
bentahar@ciise.concordia.ca \\
\and
Rabeb Mizouni\\
rabeb.mizouni@kustar.ac.ae \\
\and
Babak Khosravifar\\
babak.khosravifar@mcgill.ca \\
\and
Hadi Otrok\\
hadi.otrok@kustar.ac.ae \\
}

@@

\maketitle

First, we would like to thank and express our appreciation to the
reviewers for taking the time to carefully review our manuscript,
and for their insightful, valuable, and very useful comments. We
would like to thank the associate and chief editors as well for
their valuable comments and suggestions for improvements. We
carefully considered the comments and implemented all of them in
the revised version. In this letter, we will explain, point by
point, how the issues raised in the reviews are addressed and
answered. We hope our answers and revisions will satisfy the
reviewers and editors, which will make the paper accepted for
publication in Expert Systems With Applications Journal.\\

@@

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 1 %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
  \textbf{Reviewer 1}
\end{center}

\textbf{\underline{Reviewer}:} The presented paper is very good and up to date in the state of the art. The paper addresses a framework in which the agents use decision mechanisms in order to compete or cooperate.

\vspace{0.5cm} \textbf{\underline{1. Reviewer}:} The abstract should be shorter and it lacks information on the proposed framework and the decision mechanism based on game theory which are not mentioned. The suggested modifications aim make the abstract and the conclusion more similar.

\vspace{0.2cm}\textbf{\underline{Answer 1}: Thanks for the
comment. We made the abstract shorter and added the information about our decision making process which based on game-theoretic best response technique in the abstract.}

\vspace{0.5cm}\textbf{\underline{2. Reviewer}:}  In section 2.2 (system parameters), the authors should specify how many parameters are used before explaining them and using such parameters in the proposed mathematics. This should aid the reader in better understanding.

\vspace{0.2cm}\textbf{\underline{Answer 2}: We added a short summary about the system parameters in section 2.2. We have five system parameters and the other variables are derived or calculated based on these five parameters which are listed in Table 1. The title for Table 1. which was ``List of proposed system parameters'' was not very appropriate and we apologize for the confusion that it has caused. We changed its title to ``List of abbreviations''}

\vspace{0.5cm}\textbf{\underline{3. Reviewer}:} The text consists on very long paragraphs, mainly section 4 (experimental results), which makes the reading difficult.

@@

\vspace{0.2cm}\textbf{\underline{Answer 3}: In the revised
version, all the needed concepts are defined. Grand coalition is
defined as follows: In cooperative game theory, grand coalition is
a coalition that contains a maximum number of players as long as
they can maintain a stable (in terms of membership) and beneficial
(in terms of utility) group for all the players (Section 4.1,
paragraph 3).}

\vspace{0.5cm}\textbf{\underline{4. Reviewer}:} Still in section 4, the simulation application should be better specified, adding information on used machine, architecture, most important used services, etc.

\vspace{0.2cm}\textbf{\underline{Answer 4}: The main objective of
this work is to optimize the gain of web service communities as a
whole and to ensure the creation of stable communities in terms of
joining and leaving activities.}

\vspace{0.5cm}\textbf{\underline{5. Reviewer}:} Figure 3 is misplaced.

@@

\vspace{0.2cm}\textbf{\underline{Answer 5}: The interruption we
are mentioning can be either caused by time/memory constraints
when the number of subsets is big enough (timeout) or forced
manually by the system designer if for example the already
obtained results are satisfactory. In fact, if the algorithm gets
interrupted while verifying $depth(n)$, it will have $depth(n-1)$
already verified. Each depth will have $O(n^2)$ cases to check, so
for example if it reaches depth 10, and the algorithm gets
interrupted (manually or because of system resources), we at least
have checked for all the subsets of depth 9. Clarification has
been added in the revised manuscript at Section 4.1, last
paragraph.}

\vspace{0.5cm}\textbf{\underline{6. Reviewer}:} 6) There are some minor format errors that should be addressed.

\vspace{0.2cm}\textbf{\underline{Answer 6}: Tha
}

%\vspace{0.2cm}\textbf{\underline{Answer 9}: We 
%\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}, in}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 2 %%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2cm}

\newpage

\begin{center}
  \textbf{Reviewer 2}
\end{center}

\textbf{\underline{Reviewer}:} The paper perfectly fits within the scope of Expert Systems. This manuscript investigates the development of communities of autonomous services, formalizing the question "To compete or to cooperate?" between them. The authors do so by theorising and conducting a study through a dataset of 2,507 real services functioning on the web.

\vspace{0.5cm}\textbf{\underline{1. Reviewer}:}  Abstract: In my opinion, it is not necessary to talk about the sample used.

\vspace{0.2cm}\textbf{\underline{Answer 1}: First}

\vspace{0.5cm} \textbf{\underline{2. Reviewer}}:  Introduction: The first phrase ``Services are software systems...'' should include which kind of services are being analysed: intelligent, autonomous,... The definition used does not correspond to ``Services'' as a whole.

\vspace{0.2cm}\textbf{\underline{Answer 2}: We agree, we rephrased
the sentence as follows:  If the member $i$ is added to the set
$S$, the contribution of this set to the coalition is $v(S \cup
\left\{i\right\}) - v(S)$.}
\vspace{0.5cm} \textbf{\underline{3. Reviewer}}: Related work: The authors state in page 21: ``The interesting idea is to consider the benefits under four categories: innovation and learning,...''. If this is an interesting idea, it should be further explained. I agree with the authors, these benefits are very interesting, please provide further details.

\vspace{0.2cm}\textbf{\underline{Answer 3}: In the previous
version, the tasks were abstract. In the revised version, the
tasks are real tasks about flight booking that need to be.}

\vspace{0.5cm} \textbf{\underline{4. Reviewer}}:  Conclusion: The paper identifies clearly the implications for practice and further research. I consider the service consumer role very interesting for future research.

### 2014-01-31 papers/coop-journal-R1/coop_response_letter.tex

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 1 %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
  \textbf{Reviewer 1}
\end{center}

\textbf{\underline{Reviewer}:} The presented paper is very good and up to date in the state of the art. The paper addresses a framework in which the agents use decision mechanisms in order to compete or cooperate.

\vspace{0.5cm} \textbf{\underline{1. Reviewer}:} The abstract should be shorter and it lacks information on the proposed framework and the decision mechanism based on game theory which are not mentioned. The suggested modifications aim make the abstract and the conclusion more similar.

\vspace{0.2cm}\textbf{\underline{Answer 1}: Thanks for the
comment. We made the abstract shorter and added the information about our decision making process which is based on ``game-theoretic best response technique'' to the abstract.}

@@

\vspace{0.5cm}\textbf{\underline{2. Reviewer}:}  In section 2.2 (system parameters), the authors should specify how many parameters are used before explaining them and using such parameters in the proposed mathematics. This should aid the reader in better understanding.

\vspace{0.2cm}\textbf{\underline{Answer 2}: In the revised version, we added a short summary about the system parameters in section 2.2. We have five system parameters \emph{Task QoS}, \emph{Service QoS}, \emph{Budget}, \emph{Reputation} and \emph{Growth Factor}) and the other variables are derived or calculated based on these five parameters which are listed in Table 1. The title for Table 1. which was ``List of proposed system parameters'' was not very appropriate. We changed its title to ``List of abbreviations''}

@@

\vspace{0.5cm}\textbf{\underline{3. Reviewer}:} The text consists on very long paragraphs, mainly section 4 (experimental results), which makes the reading difficult.

\vspace{0.2cm}\textbf{\underline{Answer 3}: We edited the text in the revised version.}

@@

\vspace{0.5cm}\textbf{\underline{4. Reviewer}:} Still in section 4, the simulation application should be better specified, adding information on used machine, architecture, most important used services, etc.

\vspace{0.2cm}\textbf{\underline{Answer 4}: We agree. In the revised manuscript, we added more explanations and details about the architecture and service types. Each web service was modeled based on a class and we initiated many threads on a single process for the web services. They used abstract XML based messaging system with request parameters and a list of abstract XML based responses. Based on community task queue delay and the assigned web service quality metrics (such as reliability, throughput, latency and other metrics) these tasks will be performed with different qualities. In the experimental results and analysis section (Section 4), we have illustrated and
evaluated the average QoS of tasks performed. In the revised manuscript, we added more explanations and details about the architecture and service types.
}

@@

\vspace{0.5cm}\textbf{\underline{5. Reviewer}:} Figure 3 is misplaced.

\vspace{0.2cm}\textbf{\underline{Answer 5}: Thanks for noticing the mistake, we replaced the Figure at the correct position (we put it after the paragraph it was first mentioned on) and double checked all other figures and tables placements.}

@@

\vspace{0.5cm}\textbf{\underline{6. Reviewer}:} 6) There are some minor format errors that should be addressed.

\vspace{0.2cm}\textbf{\underline{Answer 6}: As mentioned in our Answer 4, we checked the formatting issues of paper as much as we could and we believe other formatting details will be covered the journal editors.
}

@@

\begin{center}
  \textbf{Reviewer 2}
\end{center}

\textbf{\underline{Reviewer}:} The paper perfectly fits within the scope of Expert Systems. This manuscript investigates the development of communities of autonomous services, formalizing the question "To compete or to cooperate?" between them. The authors do so by theorising and conducting a study through a dataset of 2,507 real services functioning on the web.

\vspace{0.5cm}\textbf{\underline{1. Reviewer}:}  Abstract: In my opinion, it is not necessary to talk about the sample used.

\vspace{0.2cm}\textbf{\underline{Answer 1}: True, as argued in our Answer 1 to Reviewer 1, We made the abstract more compact and removed some unnecessary details. }

@@

\vspace{0.5cm} \textbf{\underline{2. Reviewer}}:  Introduction: The first phrase ``Services are software systems...'' should include which kind of services are being analysed: intelligent, autonomous,... The definition used does not correspond to ``Services'' as a whole.

\vspace{0.2cm}\textbf{\underline{Answer 2}: We agree, the definition was too broad we rephrased
the sentence as follows: Online Services are software systems providing a standard way of
interoperability among different applications. These services are developed
 in an autonomous and intelligent manner to continuously and autonomously interact with each other to
fulfill users' requests.}

\vspace{0.5cm} \textbf{\underline{3. Reviewer}}: Related work: The authors state in page 21: ``The interesting idea is to consider the benefits under four categories: innovation and learning,...''. If this is an interesting idea, it should be further explained. I agree with the authors, these benefits are very interesting, please provide further details.

### 2014-01-31 papers/coop-journal-R1/BNJ Exp Sys App.tex
changes

\section{Introduction}\label{Introduction}
Services are software systems providing a standard way of
interoperability among different applications. They are developed
to continuously and autonomously interact with each other to
fulfill users' requests. Organizing services within virtual
structures called \emph{communities} has been proposed for the
purpose of making their discovery easier and increasing the
likelihood of their cooperation
\cite{Benatallah2003,Maamar2009,Medjahed2007,Medjahed2005}. The
idea behind communities is to gather services having similar
functionalities but distinct non-functional properties. In that
context, communities are providing pockets of expertise and
networks of services able to cooperate by substituting each other
in case of execution problems
\cite{Bentahar2008,Maamar2009,Mhamdi2012}.

@@

\subsection{System Parameters}
In this part, we demonstrate the involved parameters and their
corresponding formulations and explanations. \textbf{}

@@

In this section, we provide an empirical analysis over the
theoretical results regarding the characteristics of intelligent
service agents hosted in different communities of services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, service agents as service providers, and
master agents as community representatives. These entities are
developed with respect to what is explained in Section
\ref{Preliminaries}. In this section, the objective is to
investigate the effectiveness of the proposed strategic system on
intelligent services' overall budget and also the average quality
and quantity of tasks performed by the community of services,
which directly affects user satisfaction.
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
To verify these objectives, we study the overall performance of
the community hosting the reasoning-empowered services compared to
the ones hosting stochastic and purely competitive services. By
stochastic services, we mean services that adopt at each moment
competitive or cooperative strategies in an equally but random
way. By equally, we mean the choices are fairly divided between
the two strategies. The simulation application is written in
\textit{C\#} using \textit{Visual Studio}. Developed services are
initialized with values taken from a real dataset that includes
$2507$ real services functioning on the web. The dataset records
the QoS values of $9$ parameters including \textit{availability},
\textit{throughput}, and
\textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.

>>>>

\section{Introduction}\label{Introduction}
\textbf {Online Services are software systems providing a standard way of
interoperability among different applications. These services are developed
 in an autonomous and intelligent manner to continuously and autonomously interact with each other to
fulfill users' requests.} Organizing services within virtual
structures called \emph{communities} has been proposed for the
purpose of making their discovery easier and increasing the
likelihood of their cooperation
\cite{Benatallah2003,Maamar2009,Medjahed2007,Medjahed2005}. The
idea behind communities is to gather services having similar
functionalities but distinct non-functional properties. In that
context, communities are providing pockets of expertise and
networks of services able to cooperate by substituting each other
in case of execution problems
\cite{Bentahar2008,Maamar2009,Mhamdi2012}.

@@

\subsection{System Parameters}
In this part, we demonstrate the involved parameters and their
corresponding formulations and explanations. \textbf{Our proposed decision making process, utilizes five system parameters namely \emph{Task QoS}, \emph{Service QoS}, \emph{Budget}, \emph{Reputation} and \emph{Growth Factor}. In the following, we describe these parameters in more detail. }

@@

In this section, we provide an empirical analysis over the
theoretical results regarding the characteristics of intelligent
service agents hosted in different communities of services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, service agents as service providers, and
master agents as community representatives. These entities are
developed with respect to what is explained in Section
\ref{Preliminaries}. In this section, the objective is to
investigate the effectiveness of the proposed strategic system on
intelligent services' overall budget and also the average quality
and quantity of tasks performed by the community of services,
which directly affects user satisfaction.
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
To verify these objectives, we study the overall performance of
the community hosting the reasoning-empowered services compared to
the ones hosting stochastic and purely competitive services. By
stochastic services, we mean services that adopt at each moment
competitive or cooperative strategies in an equally but random
way. By equally, we mean the choices are fairly divided between
the two strategies. 
\textbf{The simulation application is written in
\textit{C\#} using \textit{Visual Studio} and executed the implementation on an Intel Xeon X3450 machine with 6GBs of memory.}
 Developed services are
initialized with values taken from a real dataset that includes
$2507$ real services functioning on the web. The dataset records
the QoS values of $9$ parameters including \textit{availability},
\textit{throughput}, and
\textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.
